DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-07 paper/appendix.tex
Changes to comparison and appendix

In the first method, we trained the neural network model across a set 
of 30 completed runs on the track seen in Figure~\ref{fig:track} by a
human pilot. Half of the runs saw the car driving one way along the
track, while the remaining half were of the car driving in the
opposite direction on the track.
In total, we collected 2,556 frames for training and 2,609 
frames for validation.
The weights of the network is initialized using Xavier
initializer~\cite{Glorot2010}, which is known to provide better
initial values than the random weight assignment method.
In each training step, we use a batch
size of 100 frames, which are randomly selected among all the
collected training images, to optimize the network.
We repeat this across 2,000 training steps. When a model was trained
with the  aformentioned data, the training loss was 0.0188 and the
validation  loss was 0.0132.
The change of the loss value over the course of model training can be
seen in Figure~\ref{fig:modelloss}.

@@

In the second method, we use the same data and parameters above except
that now images are labeled as 'curved' and 'straight' and we pick an
equal number of images from each category at each training step to
update the model. In other words, we try to remove bias in selecting
images. We find that the car performed better in practice by applying
this approach as the car displayed a greater ability to stay in the
center of the track (on the white tape).
However, we find that there is huge discrepency between the training
loss and the validation loss as the former was 0.09 while the latter
was 0.0869---a 10X difference---indicating that the model suffers from
the overfitting problem.

We continue to investigate ways to achieve better prediction accuracy
in training the network as well as improving the performance of the RC
car platform, especially on precise steering angle control.

@@

Another factor to consider is power supply. From our experiences, the
Pi 3 frequency throttling also kicks in when the power source can not
provide the required minimum of 2A current.
In experiments conducted with a power supply that only provided 1 Amp,
the Pi was unable to sustain a 1.2 GHz clock speed and, instead,
fluctuated between operating at 600 MHz and 1.2 GHz. As a result, it
is necessary, or at least highly recommended, that the power supply
used for the Raspberry Pi 3 be capable of outputting 2 Amps, otherwise
optimal performance isn't guaranteed.

Our initial experiment results suffered from these issues after which
we always carefully monitored the current operating frequencies of the
CPU cores during the experiments to ensure the correctness and
repeatability of the results.

>>>>

In the first method, we trained the neural network model across a set 
of 30 completed runs on the track seen in Figure~\ref{fig:track} by a
human pilot. Half of the runs saw the car driving one way along the
track, while the remaining half were of the car driving in the
opposite direction on the track.
In total, we collected 2,556 frames for training and 2,609 
frames for validation.
The weights of the network are initialized using Xavier
initializer~\cite{Glorot2010}, which is known to provide better
initial values than the random weight assignment method.
In each training step, we use a batch
size of 100 frames, which are randomly selected among all the
collected training images, to optimize the network.
We repeat this across 2,000 training steps. When a model was trained
with the  aformentioned data, the training loss was 0.0188 and the
validation  loss was 0.0132.
The change of the loss value over the course of model training can be
seen in Figure~\ref{fig:modelloss}.

@@

In the second method, we use the same data and parameters as  above 
except that now images are labeled as 'curved' and 'straight' and we pick an
equal number of images from each category at each training step to
update the model. In other words, we try to remove bias in selecting
images. We find that the car performed better in practice by applying
this approach as the car displayed a greater ability to stay in the
center of the track (on the white tape).
However, we find that there is a huge discrepency between the training
loss and the validation loss as the former was 0.09, while the latter
was 0.00869---a 10X difference---indicating that the model suffers from
the overfitting problem.

We continue to investigate ways to achieve better prediction accuracy
in training the network, as well as improving the performance of the RC
car platform, especially on precise steering angle control.

@@

Another factor to consider is power supply. From our experiences, the
Pi 3 frequency throttling also kicks in when the power source can not
provide the required minimum of 2A current.
In experiments conducted with a power supply that only provided 1 Amp,
the Pi was unable to sustain a 1.2 GHz clock speed, and instead,
fluctuated between operating at 600 MHz and 1.2 GHz. As a result, it
is necessary, or at least highly recommended, that the power supply
used for the Raspberry Pi 3 be capable of outputting 2 Amps, otherwise
optimal performance isn't guaranteed.

Our initial experiment results suffered from these issues, after which
we always carefully monitored the current operating frequencies of the
CPU cores during the experiments to ensure the correctness and
repeatability of the results.

### 2017-10-07 paper/comparison.tex
Changes to comparison and appendix

The UP Board and TX2 also perform much better when multiple DNN models
are co-scheduled. Figure~\ref{fig:sys_model} shows the results of the
multi-model co-scheduling experiment. Once again, they can comfortably
20 Hz real-time performance for all of the co-scheduled DNN control
loops, and in case of TX 2 (GPU), 100 Hz real-time control is still
feasible. Given that the GPU must be shared among the co-scheduled DNN
models, the result suggests that TX2's GPU has sufficient capacity to
accomodate multiple instances of the DNN model we tested.

@@

Another intersting observation is that TX2 (GPU) also suffers
considerable execution time increase (2.5X) despite the fact that the
co-scheduled synthetic tasks do not utilize the GPU. In other words,
the DNN model has dedicated access to the GPU. This is, however, a
known characteristic of integrated CPU-GPU architectue based
platforms that both CPU and GPU share the same memory
subsystem~\cite{Ali2017}. As a result, TX2 (GPU) fails to meet the
10ms deadline for 100 Hz control that would have been feasible if
there is no contention between the CPU cores and the GPU.

@@

In summary, we find that today's embedded computing platforms, even as
inexpensive as a Raspberry Pi 3, are powerful enough to support
vision and end-to-end deep learning based real-time control
applications. Furthermore, availability of CPU cores and GPU on these
platforms allow consolidating mutiple deep neural network based AI
workloads. However, shared resource contention among these diverse
computing resources remain an important issue that must be understood
and controlled especially for safety-critical applications.

>>>>

The UP Board and TX2 also perform much better when multiple DNN models
are co-scheduled. Figure~\ref{fig:sys_model} shows the results of the
multi-model co-scheduling experiment. Once again, they can comfortably
satisfy 20 Hz real-time performance for all of the co-scheduled DNN control
loops, and in case of TX 2 (GPU), 100 Hz real-time control is still
feasible. Given that the GPU must be shared among the co-scheduled DNN
models, the result suggests that TX2's GPU has sufficient capacity to
accomodate multiple instances of the DNN model we tested.

@@

Another intersting observation is that TX2 (GPU) also suffers
considerable execution time increase (2.5X) despite the fact that the
co-scheduled synthetic tasks do not utilize the GPU. In other words,
the DNN model has dedicated access to the GPU. This is, however, a
known characteristic of integrated CPU-GPU architectue based
platforms that both CPU and GPU share the same memory
subsystem~\cite{Ali2017}. As a result, TX2 (GPU) fails to meet the
10ms deadline for 100 Hz control that would have been feasible if
there was no contention between the CPU cores and the GPU.

@@

In summary, we find that today's embedded computing platforms, even as
inexpensive as a Raspberry Pi 3, are powerful enough to support
vision and end-to-end deep learning based real-time control
applications. Furthermore, availability of CPU cores and GPU on these
platforms allow consolidating mutiple deep neural network based AI
workloads. However, shared resource contention among these diverse
computing resources remains an important issue that must be understood
and controlled, especially for safety-critical applications.
